\headingfont University of Extremadura\\ Faculty of Science\\[1cm] \textbf{ Physics degree\\ Degree Final Project\\[3cm] \flushleft{\large{About implementation of LoRa-based wireless monitoring systems for tree species dendrometry.}}\\[3cm] }

### 2020-06-15 docs/paper/LaTex/Paper.tex
Completes paper.tex

% To improve headers an footers (I'm using to set page number at right)
\usepackage{fancyhdr}
% Turn on the style
\pagestyle{fancy}
\fancyhf{} % Start with clearing everything in the header and footer
\renewcommand{\headrulewidth}{0pt} % Removes the horizontal rule in header by default
\fancyfoot[R]{\thepage} % Set the right side of the footer to be the page number

@@

Once is available the remote control for Raspberry Pi through ssh, is possible to manage it completely from the command line, even upgrade the system and compile the required controller to get properly working the LoRa transceiver. At this point and depending on the type of access point used to provide internet service to the Raspberry, the reader will be able even to remote control the Raspberry over internet. For this purpose could be useful to read the access point documentation in order to perform port forwarding or alternatively \href{http://www.thirdway.ch/En/projects/raspberry_pi_3g/index.php}{a reverse tunnel over ssh.}\footnote{In the case the ISP does not allow ssh when using a GSM module, also the reader may find that IPv6 works but IPv4 does not. Anyway, as said the internet access point could be variable and it is not determined by this project.\\ The most important thing is to work comfortably with the Raspberry Pi with no HDMI, keyboard and mouse plugged, and this can be done locally in a LAN to configure it in a first place.}

>>>>

% To improve headers an footers (I'm using to set page number at right)
\usepackage{fancyhdr}
% Turn on the style
\pagestyle{fancy}
\fancyhf{} % Start with clearing everything in the header and footer
\renewcommand{\headrulewidth}{1pt} % Removes the horizontal rule in header by default
\fancyfoot[R]{\thepage} % Set the right side of the footer to be the page number
\fancyhead[R]{\rightmark}
\setlength{\headheight}{14pt}% ...at least 51.60004pt

@@

Once is available the remote control for Raspberry Pi through ssh, is possible to manage it completely from the command line, even upgrade the system and compile the required controller to get properly working the LoRa transceiver.

At this point and depending on the type of access point used to provide internet service to the Raspberry, the reader will be able even to remote control the Raspberry over internet. For this purpose could be useful to read the access point documentation in order to perform port forwarding or alternatively \href{http://www.thirdway.ch/En/projects/raspberry_pi_3g/index.php}{a reverse tunnel over ssh} ---in the case the ISP does not allow ssh when using a GSM module, also the reader may find that IPv6 works but IPv4 does not. Anyway, as said the internet access point could be variable and it is not determined by this project.\footnote{The most important thing is to work comfortably with the Raspberry Pi with no HDMI, keyboard and mouse plugged, and this can be done locally in a LAN to configure it in a first place.}
